---
title: "Library GtrendsR "
author: "Krushang Shah"
date: "6/25/2020"
output:
  html_document:
    df_print: paged
    toc: yes
    toc_depth: '3'
  pdf_document:
    toc: yes
    toc_depth: 3
---
# Library gtrendsr

The library gtrendsr can be used in order to extract the trends data into a data frame, which can then be used for the predictions you want.

The documentation for the library can be found here [gtrendsR](https://cran.r-project.org/package=gtrendsR)
## Setup
```{r setup, warning=FALSE, message=FALSE}
library(scales)
library(tidyverse)
library(broom)
library(readxl)
library(zoo)
theme_set(theme_bw())

knitr::opts_chunk$set(
	echo = TRUE,
	message = FALSE,
	warning = FALSE
)
```

## Install the library

install.packages("gtrendsR")
```{r}
library(gtrendsR)
```
## Explanation

gtrends(
  keyword = NA,
  geo = "",
  time = "today+5-y",
  gprop = c("web", "news", "images", "froogle", "youtube"),
  category = 0,
  hl = "en-US",
  low_search_volume = FALSE,
  cookie_url = "http://trends.google.com/Cookies/NID",
  tz = 0,
  onlyInterest = FALSE
)

## Usage
You can provide keywords, location, time and category.
The category number can also be found from the URL that results after the search you made
```{r}
tmp <- gtrends(,geo="US",category = 467,time = "all")
tmp[["interest_over_time"]]
```
## Related Topics and Queries

```{r}
tmp[["related_topics"]]
tmp[["related_queries"]]
```

